---
surname: 毕顺
profilepic: "photo.jpg"
position: "博士研究生"
address: "南京师范大学 地理科学学院"
phone: "+86 156 5190 9539"
email: "bishun1994@foxmail.com"
researchgate: Shun_Bi
twitter: bishun945
github: bishun945
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
# output: vitae::markdowncv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Research Interests

My current interest is to build an algorithm blending framework for estimating optical active constitutes, such as Chlorophyll-a concentration, across Case I and II waters from remote sensing data. 

My other interests include building Chla algorithms for specific water types (e.g., turbid Case II waters), column-integrated algal biomass for inland lakes, atmospheric correction, and data gap-filling for satellite imagery.

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where,
  "BSc", "2012 - 2016", "School of Geography, Geomatics and Planning, Jiangsu Normal University", "Jiangsu, Xuzhou",
  "Ms", "2016 - 2018", "School of Geography, Nanjing Normal University", "Jiangsu, Nanjing",
  "Ph.D.", "2018 - Now", "School of Geography, Nanjing Normal University", "Jiangsu, Nanjing"
) %>% 
  detailed_entries(Degree, Year, Institution, Where)
```

# Awards and Honors

```{r}
tribble(
  ~Year,  ~Desc, ~Location,
  "Jun-2017", "the Third Prize of 2017 NNU Graduate Mathematical Modeling Competition", "China",
  "Dec-2017", "the Second Prize of 2017 National Graduate Mathematical Modeling Competition", "China",
  "Nov-2018", "ESA-MOST China Dragon 4 Cooperation: BEST POSTER AWARD", "China",
  "Apr-2019", "the Third Prize of the 6th Sharing Cup College Student Science and Technology Resources sharing serveice innovation competition", "China",
  "Oct-2019", "the First Prize of the 1st Hyerspectral Imagery Processing Competition - Orbit Cup", "China" 
) %>% 
  brief_entries(
    when = Year, 
    what = Desc,
    with = Location
  )
```

# Grants and Fellowships

```{r}
tribble(
  ~Year,  ~Desc, ~With,
  "Dec-2018", "the Postgraduate Research & Practice Innovation Program of Jiangsu province, China", "Grant: KYCX18-1205",
  "Sep-2017", "the Second Prize Scholarship of 2016", "China", 
  "Sep-2018", "the First Prize Scholarship of 2017",  "China", 
  "Sep-2019", "the First Prize Scholarship of 2018", "China", 
  "Nov-2019", "the Scholarship of Saiteng Fenghui of 2019",  "China", 
  "Sep-2020", "the First Prize Scholarship of 2019", "China", 
  "Nov-2020", "the National Scholarship of 2020", "China"
) %>% 
    brief_entries(
    when = Year, 
    what = Desc,
    with = With
  )
```

# Publications

## Peer-reviewed journal articles  

```{r}
bibliography_entries("publications.bib")
```

## R Packages

```{r}
bibliography_entries("packages.bib")
```

# Conferences

```{r}
tribble(
  ~Year,  ~Desc, ~Location,
  "May-2017", "Jiangsu University Geography Postgradutae Forum (2017)", "Jiangsu, Nanjing",
  "Sep-2017", "the 5th Graduate Forum of Jiangsu Society of Oceanology and Lomnology", "Jiangsu, Nanjing",
  "Oct-2017", "the 1st China Plateau Lake Forum", "Yunnan, Kunming",
  "Apr-2018", "Jiangsu University Geography Postgradutae Forum (2018)", "Jiangsu, Nanjing",
  "Nov-2018", "ESA-MOST DRAGON 4 PROGRAMME - Advanced Training Course in Ocean & Coastal Remote Sensing", "Guangdong, Shenzhen",
  "Nov-2018", "National Forum for Doctoral Students in Geographic Information Science (2018)", "Jiangsu, Nanjing",
  "Nov-2018", "the 18th Water Color Remote Sensing Conference in China", "Guangdong, Zhanjiang",
  "Aug-2019", "the 1st Wetland Remote Sensing Conference in China", "Jilin, Changchung",
  "Nov-2019", "the 19th Water Color Remote Sensing Conference in China", "Hainan, Sanya",
  "Aug-2020", "the 2nd Wetland Remote Sensing Conference in China", "Online",
  "Dec-2020", "National Forum for Doctoral Students in Geographic Information Science (2020)", "Online"
) %>% 
    brief_entries(
    when = Year, 
    what = Desc,
    with = Location
  )
```

# Languages

Mandarin (native), English (written and oral)

# Skills

#### Programming skills

R, Python, IDL, MATLAB

#### Operating systems

Windows, Linux (Ubuntu), macOS

#### Remote sensing processing tools

SeaDAS, SNAP, QGIS, POLYMER, ACOLITE, ENVI, GEE, Hydro/EcoLight

#### Experiment skills

Apparent optical properties collection: ASD HH2, TriOS RAMSES; Inherent optical properties collection: HydroScat-6, LISST-100X; Quantitative filter technique.

# References

Yunmei Li, Ph.D., Professor 

School of Geography

Nanjing Normal University, Nanjing, China

+86 138 1383 3136

liyunmei@njnu.edu.cn


